DynaProg for Scala

### 2013-01-03 docs/report/design.tex
More report.

{\center\color{red} XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX\\ CONTINUE HERE\\ XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX}

Although our compilation stack might look quite similar to that of Delite, we do not share any component but LMS for the user functions. The compilation and execution process works as follows:\ul
% XXX: Macros ?
\item At compilation time:\ul
	\item LMS generates the C code corresponding to the user-defined function and embeds it into the program
	\ule
\item At run-time, per problem description instance\ul
	\item Recurrence analysis 
	\item Code generation
	\ule
\item At run-time, per problem instance function call\ul
	\item Adaptation of code to problem dimensions
	\item Compilation of CUDA and C/JNI code as an external library (jnilib) then loaded
	\item Compilation of a Scala wrapper to invoke the generated code
	\item Execution of the compiled code:
		\[ \text{Scala wrapper} \iff \text{JNI interface} \iff \text{CPU C code} \iff \text{CUDA kernel}\]
	\ule
\ule

>>>>

Although our compilation stack might look quite similar to that of Delite, we do not share any component but LMS for the user functions generation. The compilation and execution process works as follows:\ul
\item Compilation: LMS generates the C code corresponding to the user-defined function and embeds them into the program bytecode (note that we present them separately for clarity).
\item Runtime, for each parser (grammar+algebra): recurrences analysis is done in order to generate code (with placeholders for constants)
\item Runtime, at every parse function call: the input size is known, hence replaced into the generic problem code, which is then processed by CUDA, C++ and Scala compilers. Then the JNI library resulting of the compilation is loaded and its corresponding Scala wrapper is invoked on the data to be processed.
\ule

\begin{figure}[H]\begin{center}\setlength{\unitlength}{.6cm}\begin{picture}(15,19)
\put(0,17){\tbox{5}{1}{DSL libraries}}\put(6,17){\tbox{5}{1}{User program}}
{\linethickness{1.5pt}\moveto(8,17)\lineto(8,16.25)\lineto(2.5,16.25)\strokepath\put(2.5,17){\vector(0,-1){2}}}\put(-1.5,16){\small Scala compiler}
\put(8.5,17){\linethickness{1.5pt}\vector(0,-1){2}}\put(8.75,16){\small LMS}
% -----
\put(0,14){\tbox{5}{1}{JVM bytecode}}\put(6,14){\tbox{5}{1}{C functions}}
\put(2.5,14){\vector(0,-1){2.75}}\put(8.5,14){\vector(0,-1){1.75}}
\multiput(-2,13)(.15,0){130}{\circle*{.05}}\put(14,13.25){\small compilation}\put(14,12.5){\small run-time}
% -----
{\linethickness{1.5pt}\moveto(2.5,7)\lineto(2.5,11)\lineto(5,11)\strokepath\put(5,11){\vector(1,0){1}}}
\put(2.75,9){\small recurrences analysis}\put(2.75,8.4){\small code generation}
% -----
\put(6,10){\tbox{5}{2}{C/CUDA/JNI code}}
\put(8.5,10){\linethickness{1.5pt}\vector(0,-1){3}}\put(8.75,9){\small constants evaluation}\put(8.75,8.4){\small compilation}
{\linethickness{1.5pt}\moveto(12,1.5)\lineto(12,8)\lineto(10,8)\strokepath\put(10,8){\vector(-1,0){1.5}}}\put(12.25,6.5){\rotatebox{-90}{\small input size}}
% -----
\put(0,2.5){\tbox{5}{4.5}{Scala parsers}}
\put(6,2.5){\put(0,0){\tbox{5}{4.5}{}}
	\put(.25,3.25){\tbox{4.5}{1}{CUDA kernels}}\put(.25,1.75){\tbox{4.5}{1}{JNI / host C}}\put(.25,.25){\tbox{4.5}{1}{Scala wrapper}}
	\put(3.5,3.25){\vector(0,-1){.5}}\put(3.5,1.75){\vector(0,-1){.5}}\put(1.5,1.25){\vector(0,1){.5}}\put(1.5,2.75){\vector(0,1){.5}}}
\put(13,1){\tbox[l0]{4}{1}{Input data}}
\put(13,0){\tbox[l0]{4}{1}{Output data}}
\put(1.5,1.5){\vector(0,1){1}}\put(7.5,1.5){\vector(0,1){1}}\moveto(1.5,2)\lineto(1.5,1.5)\lineto(13,1.5)\strokepath % input
\put(9.5,.5){\line(0,1){2}}\moveto(3.5,2.5)\lineto(3.5,.5)\lineto(12,.5)\strokepath\put(12,.5){\vector(1,0){1}} % output

\end{picture}\end{center}\caption{Compilation and execution scheme of a parser}\end{figure}

### 2013-01-03 docs/report/implementation.tex
More report.

\newpage
\section{Implementation}

% ------------------------------------------------------------------------------------------------
\subsection{CUDA ad-hoc}
During the first phase of project, and after the decision to focus on non-serial problems implementation on GPU, we developed an ad-hoc version of 3 non-serial problems. Since we erroneously complicated the matrix of the polygon triangulation problem, we devised 3 different matrix shape, that is upper triangular for single-track problems, rectangular for two-track problems and parallelogram for the polygon triangulation.

>>>>

\newpage
\section{Implementation}
% ------------------------------------------------------------------------------------------------
\subsection{CUDA ad-hoc}
In the project planning, an ad-hoc implementation phase immediately followed the problem analysis. The goals of this phase is threefold:\ol
\item Better understand the challenges in CUDA implementation of dynamic programming problems and get on par with state-of-art implementations.
\item Have a baseline implementation that is independent of the hardware and that could be benchmarked. We also tried to contact the authors of \cite{swat_mega} and \cite{gpu_atlp} to obtain their implementation. The former provided us with their implementation, which turned out to address large serial problems whereas our focus was on smaller non-serial problems, the latter did not respond to our solicitations.
\item Have an optimal implementation that can serve as target to be imitated and generalized by the code generation.
\ole

{\center\color{red} XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX\\ CONTINUE HERE\\ XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX}

The project development was scheduled in \ul
\item Problems analysis
\item Ad-hoc implementation (CUDA)
\item Porting ADP parsers
\item Improving parsers / adding functionalities
\item Integrating CUDA generation into parsers
\ule

During the first phase of project, and after the decision to focus on non-serial problems implementation on GPU, we developed an ad-hoc version of 3 non-serial problems. Since we erroneously complicated the matrix of the polygon triangulation problem, we devised 3 different matrix shape, that is upper triangular for single-track problems, rectangular for two-track problems and parallelogram for the polygon triangulation.
